Reasonably Programmable Literal Notation

### 2018-06-25 icfp18/syntax-icfp18.tex
added brief mention of dirty macros paper

It is  possible in many production-grade hygienic macro systems, e.g. in Racket \cite{Flatt:2012:CLR:2063176.2063195}, for a macro to granularly opt out of the hygiene discipline in parts of an expansion, but clients cannot be sure that this powerful ``escape hatch'' was used in a disciplined way. However, a typed literal macro system could be implemented as a layer on top of an existing hygienic macro system, e.g. in Racket, by internally deploying the escape hatch exactly as specified by this paper. %From the macro expander's perspective, it has appeared by magic''.

>>>>

It is  possible in many production-grade hygienic macro systems, e.g. in Racket \cite{Flatt:2012:CLR:2063176.2063195}, for a macro to granularly opt out of the hygiene discipline in parts of an expansion \cite{kiselyov2002write}, but clients cannot be sure that this powerful ``escape hatch'' was used in a disciplined way. However, a typed literal macro system could be implemented as a layer on top of an existing hygienic macro system, e.g. in Racket, by internally deploying the escape hatch exactly as specified by this paper. %From the macro expander's perspective, it has appeared by magic''.
